Supplementary Materials

### 2018-03-27 paper/appendix_modelDescription.tex
add citation for description
add missing citation

\taoli{Do we need citation in Appendix?}

\textbf{Comment} We used the same network setting in the Decomposable Attention paper (cite). That are, network hidden size is $200$; input word embeddings are $200$ embeddings (downsampled from $300$ dimensional GloVe embeddings (cite) by a learnable linear layer); dropout (cite) is $0.2$ for learning; and learning rate is $0.05$.

@@

\end{lstlisting}

\end{document}

>>>>

%\taoli{Do we need citation in Appendix?}

\textbf{Comment} We used the same network setting in the Decomposable Attention paper~\cite{parikh2016emnlp}. That are, network hidden size is $200$; input word embeddings are $200$ embeddings (downsampled from $300$ dimensional GloVe embeddings~\cite{PenningtonSocherManning2014} by a learnable linear layer); dropout~\cite{SrivastavaHinton2014} is $0.2$ for learning; and learning rate is $0.05$.

@@

\end{lstlisting}
\bibliographystyle{abbrv-doi}
%\bibliographystyle{abbrv-doi-narrow}
%\bibliographystyle{abbrv-doi-hyperref}
%\bibliographystyle{abbrv-doi-hyperref-narrow}

\bibliography{entailVis.bib}
\end{document}
